% Define the terms
\nomenclature{\textsc{2-d/3-d}}{Two-dimensional/tri-dimensional.}
\nomenclature{\textsc{afni}}{Analysis of Functional Neuroimages.}
\nomenclature{\textsc{asl}}{Arterial spin labelling.}
\nomenclature{\textsc{bmi}}{Body mass index.}
\nomenclature{\textsc{cca}}{Canonical correlation analysis.}
\nomenclature{\textsc{cmv}}{Classical multivariate test.}
\nomenclature{\textsc{ctp}}{Closed testing procedure.}
\nomenclature{\textsc{doi}}{Digital object identifier.}
\nomenclature{\textsc{dz}}{Dizygotic twin.}
\nomenclature{\textsc{eb}}{Exchangeability block.}
\nomenclature{\textsc{ee}}{Exchangeable errors.}
\nomenclature{\textsc{ise}}{Independent and symmetric errors.}
\nomenclature{\textsc{fdr}}{False discovery rate.}
\nomenclature{\textsc{film}}{\textsc{fmrib}'s Improved Linear Model}
\nomenclature{\textsc{flame}}{\textsc{fmrib}'s Local Analysis of Mixed Effects.}
\nomenclature{\textsc{fmri}}{Functional magnetic resonance imaging.}
\nomenclature{\textsc{fmrib}}{Oxford Centre for Functional \textsc{mri} of the Brain.}
\nomenclature{\textsc{fs}}{FreeSurfer.}
\nomenclature{\textsc{fsl}}{\textsc{fmrib} Software Library.}
\nomenclature{\textsc{fwer}}{Familywise error rate.}
\nomenclature{\textsc{fwhm}}{Full-width at half-maximum.}
\nomenclature{\textsc{gev}}{Generalised extreme value distribution.}
\nomenclature{\textsc{glm}}{General linear model.}
\nomenclature{\textsc{gpd}}{Generalised Pareto distribution.}
\nomenclature{\textsc{gpl}}{General Public License.}
\nomenclature{\textsc{gpu}}{Graphics processing unit.}
\nomenclature{\textsc{hcp}}{Human Connectome Project.}
\nomenclature{\textsc{ic}3/\textsc{ic}5/\textsc{ic}7}{Icosahedron recursively subdivided 3, 5 or 7 times.}
\nomenclature{\textsc{ise}}{Independent and symmetric errors.}
\nomenclature{\textsc{iut}}{Intersection-union test.}
\nomenclature{\textsc{jnh}}{Joint null hypothesis.}
\nomenclature{\textsc{manova}/\textsc{mancova}}{Multivariate analysis of variance/covariance.}
\nomenclature{\textsc{mni}}{Montreal Neurological Institute.}
\nomenclature{\textsc{mprage}}{Magnetization-prepared rapid gradient-echo.}
\nomenclature{\textsc{mri}}{Magnetic resonance imaging.}
\nomenclature{\textsc{msm}}{Multi-modal surface matching.}
\nomenclature{\textsc{mz}}{Monozygotic twin.}
\nomenclature{\textsc{npc}}{Non-parametric combination.}
\nomenclature{\textsc{ns}}{Non-sibling.}
\nomenclature{\textsc{ora}}{Oxford Research Archive.}
\nomenclature{\textsc{palm}}{Permutation Analysis of Linear Models.}
\nomenclature{\textsc{pet}}{Positron-emission tomography.}
\nomenclature{\textsc{rft}}{Random field theory.}
\nomenclature{\textsc{roi}}{Region of interest.}
\nomenclature{\textsc{sd}}{Spherical Demons.}
\nomenclature{\textsc{se}}{Standard error.}
\nomenclature{\textsc{solar}}{Sequential Oligogenic Linkage Analysis Routines.}
\nomenclature{\textsc{svd}}{Singular value decomposition.}
\nomenclature{\textsc{tfce}}{Threshold-free cluster enhancement.}
\nomenclature{\textsc{uit}}{Union-intersection test.}
\nomenclature{\textsc{url}}{Uniform resource locator.}
\nomenclature{\textsc{vbm}}{Voxel-based morphometry.}
\nomenclature{\textsc{vg}}{Variance group.}
\nomenclature{\textsc{vlbw}}{Very-low birth weight.}
\nomenclature{\textsc{wm}}{White matter.}

% This will actually print the above terms
\printnomenclature[4cm]